High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-04-06 notebooks/mnist.qmd
resnet

```{julia}
epochs = 100
clf = NeuralNetworkClassifier(
    builder=MLJFlux.MLP(hidden=(32,), σ=relu), 
    epochs=epochs,
    batch_size=Int(round(n_obs/10))
)
conf_model = conformal_model(clf; method=:simple_inductive)
mach = machine(conf_model, X, labels)
fit!(mach)
```

```{julia}
M = CCE.ConformalModel(mach.model, mach.fitresult)
```

@@

```{julia}
using CounterfactualExplanations.DataPreprocessing: undersample
dt_reduced = undersample(counterfactual_data, 100)
# dt_reduced = counterfactual_data
```

@@

# Generate counterfactual using CCE generator:
generator = CCEGenerator(
    λ=[0.0,10.0], 
    temp=0.01, 
    # opt=CounterfactualExplanations.Generators.JSMADescent(η=5.0),
)
ce_conformal = generate_counterfactual(
    x, target, dt_reduced, M, generator; 
    decision_threshold=γ, max_iter=T,
    initialization=:identity,
    converge_when=:generator_conditions,
)
```

```{julia}
p1 = Plots.plot(
    convert2image(MNIST, reshape(x,28,28)),
    axis=nothing, 
    size=(img_height, img_height),
    title="Factual"
)
plts = [p1]

@@

>>>>

First, let's create a couple of image classifier architectures:

```{julia}
epochs = 100
batchsize = Int(round(n_obs/10))

# Simple MLP:
mlp = NeuralNetworkClassifier(
    builder=MLJFlux.MLP(hidden=(32,), σ=relu), 
    epochs=epochs,
    batch_size=batchsize,
)

# Deep Ensemble:
mlp_ens = EnsembleModel(model=mlp, n=5)

# ResNet:
using MLJFlux, Metalhead
builder = MLJFlux.image_builder(ResNet, 18, pretrain=true)
resnet = ImageClassifier(
    builder=builder,
    epochs=epochs,
    batch_size=batchsize,
)

# ResNet Ensemble:
resnet_ens = EnsembleModel(model=resnet, n=5)
```

```{julia}

conf_model = conformal_model(mlp; method=:adaptive_inductive, coverage=.99)
mach = machine(conf_model, X, labels)
fit!(mach)
M = CCE.ConformalModel(mach.model, mach.fitresult)
```

@@

@@

# Generate counterfactual using CCE generator:
generator = CCEGenerator(
    λ=[0.0,10.0], 
    temp=0.01, 
    # opt=CounterfactualExplanations.Generators.JSMADescent(η=0.5),
)
ce_conformal = generate_counterfactual(
    x, target, dt_reduced, M, generator; 
    decision_threshold=γ, max_iter=T,
    initialization=:identity,
    converge_when=:generator_conditions,
)

# Plot:
p1 = Plots.plot(
    convert2image(MNIST, reshape(x,28,28)),
    axis=nothing, 
    size=(img_height, img_height),
    title="Factual"
)
plts = [p1]

@@

## Benchmark

```{julia}
# Benchmark generators:
generators = Dict(
    :wachter => GenericGenerator(opt=opt, λ=l2_λ),
    :revise => REVISEGenerator(opt=opt, λ=l2_λ),
    :greedy => GreedyGenerator(),
)

# Conformal Models:

# Measures:
measures = [
    CounterfactualExplanations.distance,
    CCE.distance_from_energy,
    CCE.distance_from_targets,
    CounterfactualExplanations.validity,
]
```
